---
title: "EEB603_GitTutorial"
author: "Jacob Heil, Lauren Hunt, Katie Murenbeeld"
date: "10/18/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Part One: Introduction and Installation

## 1. Introduction: Why Git and GitHub?
### What's the difference between Git and GitHub.
Git is a **version control system** that is like a supped up version of the "Track Changes" feature within Microsoft Word. Git allows the different collaborators on a project to track changes and revert to older versions if needed. 

GitHub is a cloud based platform built around Git that stores code *__pushed__* to it from a computer that uses Git.


## 2. Register for a GitHub Account

If you do not currently have a GitHub account then you will register for one today! If you already have a GitHub account, sit back and relax while your classmates get set up.

1. Go to https://github.com
2. Pick a username that incorporates your actual name. Enter an email and create a password.
3. Select a plan: Free is all you will likely need.
4. (optional) Answer a few questions about your code skill level, plans for using GitHub, and lost some interests.
5. You'll get a verification email. 
6. When you click the link from the Verification you will be taken to your new GitHub account with the option to create your first repository or *repo*. Do not make one yet. We will come back to that. 

## 3. Upgrade R and RStudio
We all have R and RStudio on our own computers by now, but here you can check your version and upgrade if needed.

```{r}
R.version.string
```

If you would like to update your current R packages you can use the following command:

```{r}
#update.packages(ask = FALSE, checkBuilt = TRUE)
```

## 4. Install Git
Open up the terminal or shell and check to see if you already git installed.

```{bash}
which git
git --version
```


## 5. Bonjour Git, enchante

## 6. Optional: Install a Git client




